---
title: "Vignette illustrating the use of grpRR in logisitic regression"
author: "Britta Velten"
date: "`r Sys.Date()`"
output:
  BiocStyle::html_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Example_scMT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, message=FALSE, warning=FALSE}
library(grpRR)
library(ggplot2)
```

Note that the implementation of logistic regression is still experimental in some parts.

# Make example data with four groups
Create an example data set with 4 groups, 400 samples and 800 features.
```{r}
set.seed(1234)
data <- makeExampleData(n = 100, p=320, g=4, pis=c(0.05,0.1,0.05,0.1),
                        gammas=c(0.1,0.1,10,10), response = "bernoulli")
```

# Fit the model
`fit_grpRR` is the main function of this package, which allows to fit the proposed Bayesian models with different settings on the prior (by setting `spikeslab` to FALSE or TRUE) and the variational approximation (by setting `factoriseQ` to FALSE or TRUE). By default, the model is fit with a sparsity promoting spike-and-slab prior and a fully-factorised mean-field assumption. The ELBO is currently not calculated in the logisitc regession framework.
```{r}
fit <- fit_grpRR(data$X, data$y, data$annot, verbose = FALSE,
                 family = "binomial", calcELB=FALSE)
```

# Posterior distribtions
The VB approach directly yields posterior distributions for each parameter. Note, however, that using VB these are often too concentrated and can not be directly used for construciton of confidence intervals etc. However, they can provide good point estimates.
```{r}
plotPosterior(fit, "gamma", gamma0 = data$gammas)
plotPosterior(fit, "pi", pi0 = data$pis)
```

# Model coefficients and intercept
The estimated coefficients and intercept are contained in the result list.
```{r}
# get coefficients
beta <- fit$EW_beta
# plot estimated versus true beta
qplot(beta, data$beta)
```

```{r}
# get intercept
intercept <- fit$intercept
```


# Comparison to other methods
Using the functions `cv_compare` or `runMethods` the grpRR method can be compared to various related regression methods.
Some standard methods like Lasso and Ridge are always included in the comparison. Other methods can be added via the options of `cv_compare`.
`cv_compare` uses a cross-validation scheme to train and evaluate the different methdods.
`runMethods` can be used to  train different methods on the full data witout evaluation.
For time reasons we take a small number of folds in this illustration and only include the most common methods for comparison.
```{r}
comp <- cv_compare(data$X, data$y, data$annot,
           nfolds = 3, plot_cv = FALSE, verbose=FALSE,
           family = "binomial")
plotMethodComparison(comp, methods2plot = c("grpRR_SS", "Lasso"), family = "binomial")
```

#SessionInfo
```{r}
sessionInfo()
```

